Guided Proofreading of Automatic Segmentations for Connectomics

### 2016-11-14 paper/evaluation.tex

We evaluate guided proofreading on multiple different real-world connectomics datasets of different species. We perform experiments for error correction based on a selection oracle, automatic selection with threshold, and the forced choice setting. The latter is designed as a between-subjects user study with novice and expert participants.

@@

The following serial section electron microscopy datasets are used for the evaluation of our method. 
\\~\\
\textbf{L. Cylinder.} We use the left part of the 3-cylinder mouse cortex volume of Kasthuri \etal~\cite{kasthuri2015saturated} ($2048\times2048\times300$ voxels). The tissue is dense mammalian neuropil from layers 4 and 5 of the S1 primary somatosensory cortex of a healthy mouse. The resolution of our dataset is $3\times3\, \text{nm}^2$ per pixel, and the section thickness is $30\, \text{nm}$. The image data and a manually-labeled expert segmentation is publicly available as ground truth for the entire dataset\footnote{The Kasthuri 3-cylinder mouse cortex volume is available at  https://software.rc.fas.harvard.edu/lichtman/vast/.}.
\\~\\
\textbf{AC4 subvolume.} This dataset is part of a publicly available dataset of mouse cortex that was published for the ISBI 2013 challenge "SNEMI3D: 3D Segmentation of neurites in EM images". The resolution of this dataset is $6\times6\times30~\text{nm}^3\text{/voxel}$. Haehn~\etal cut the most representative subvolume ($400\times400\times10$ voxels) of this dataset with respect to the distribution of object sizes~\cite{haehn_dojo_2014}. This subvolume was used for Haehn~\etal~experiment on interactive proofreading tools for connectomics. The data, labeled ground truth and findings of their study are published online\footnote{The AC4 subvolume and results of the interactive proofreading experiment are available at http://rhoana.org/dojo/.}. 
\\~\\
\textbf{CREMI A/B/C.} As part of the MICCAI 2016 challenge on circuit reconstruction from electron microscopy images (CREMI) six datasets (each $1250\times1250\times125$ voxels) were made publicly available\footnote{The MICCAI CREMI challenge data is available at http://www.cremi.org.}. Since only three include manually labeled ground truth, we use these three volumes for our experiments. The volumes are part of adult fruit fly (Drosophila melanogaster) brain. The resolution of all three datasets is $4\times4\times40~\text{nm}^3\text{/voxel}$. 
\\~\\
\textbf{Automatic segmentation pipeline.}
We use a state-of-the-art method to create a dense automatic segmentation of the data. Membrane probabilities are generated using a convolutional neural network based on the U-net architecture~\cite{RonnebergerFB15}. The probabilities are used to seed watershed and generate an oversegmentation using superpixels. Agglomeration is then performed by the GALA active learning classifier~\cite{nunez2014graph}.

@@

To train our split error classifier, we use the L. Cylinder dataset. We use the first 250 sections of the data for training and validation. For n-fold cross validation, we select one quarter of this data and re-select after each epoch. We minimize cross-entropy loss and update using stochastic gradient descent with Nesterov momentum \cite{nesterov}.
To generate training data, we identify correct regions and split errors in the automatic segmentation by intersection with ground truth regions. This is required since extracellular space is not labeled in the ground truth but in our dense automatic segmentation. 
From these regions, we sample 112,760 correct and 112,760 split error patches with 4-channels as described above. The patches are normalized and to further augment our training data, we rotate patches within each mini-batch by $k*90$ degrees with randomly chosen $k$. The training parameters such as filter size, number of filters, learning rate, and momentum are the result of intuition and experience, studying recent machine learning research as well as a brute force parameter search within a limited range (see supplementary material). 
The final parameters are listed in the first row of table~\ref{tab:parameters}. Our CNN configuration results in approximately 170,000 learnable parameters. We assume that training has converged if the validation loss does not decrease for 50 epochs. We test the CNN by generating a balanced set of 8,780 correct and 8,780 error patches using unseen data of the left cylinder dataset and report testing results in the second row of table~\ref{tab:parameters}.

@@

\subsection{Baseline comparison}

\textbf{Interactive proofreading.} According to the comparison of Haehn~\etal~, the best performing proofreading tool for novices is Dojo~\cite{haehn_dojo_2014}. We use the publicly available findings of their user study as a baseline comparison. More specifically, we use the data of the Dojo user with the reported best performance.

\textbf{Computer-aided proofreading.}

>>>>

We evaluate guided proofreading on multiple different real-world connectomics datasets of different species. All datasets were acquired using either via serial section electron microscopy (ssEM) or serial section transmission electron microscopy (ssTEM). We perform experiments for error correction based on a selection oracle, automatic selection with threshold, and the forced choice setting. The latter is designed as a between-subjects user study with novice and expert participants.

@@

\textbf{L. Cylinder.} We use the left part of the 3-cylinder mouse cortex volume of Kasthuri \etal~\cite{kasthuri2015saturated} ($2048\times2048\times300$ voxels). The tissue is dense mammalian neuropil from layers 4 and 5 of the S1 primary somatosensory cortex of a healthy mouse and was acquired using ssEM. The resolution of our dataset is $3\times3\, \text{nm}^2$ per pixel, and the section thickness is $30\, \text{nm}$. The image data and a manually-labeled expert segmentation is publicly available as ground truth for the entire dataset\footnote{The Kasthuri 3-cylinder mouse cortex volume is available at  https://software.rc.fas.harvard.edu/lichtman/vast/.}.
\\~\\
\textbf{AC4 subvolume.} This dataset is part of a publicly available dataset of mouse cortex that was published for the ISBI 2013 challenge "SNEMI3D: 3D Segmentation of neurites in EM images". The resolution of this dataset is $6\times6\times30~\text{nm}^3\text{/voxel}$ and it was acquired using ssEM. Haehn~\etal found the most representative subvolume ($400\times400\times10$ voxels) of this dataset with respect to the distribution of object sizes~\cite{haehn_dojo_2014}. This subvolume was used for Haehn~\etal~experiment on interactive proofreading tools for connectomics. We use the data, labeled ground truth and findings of their study which are published online\footnote{The AC4 subvolume and results of the interactive proofreading experiment are available at http://rhoana.org/dojo/.}. 
\\~\\
\textbf{CREMI A/B/C.} As part of the MICCAI 2016 challenge on circuit reconstruction from electron microscopy images (CREMI) six ssTEM datasets (each $1250\times1250\times125$ voxels) were made publicly available\footnote{The MICCAI CREMI challenge data is available at http://www.cremi.org.}. Since only three include manually labeled ground truth, we use these three volumes for our experiments. The volumes are part of adult fruit fly (Drosophila melanogaster) brain. The resolution of all three datasets is $4\times4\times40~\text{nm}^3\text{/voxel}$. 
\\~\\
\textbf{Automatic segmentation pipeline.}
We use a state-of-the-art method to create a dense automatic segmentation of the data. Membrane probabilities are generated using a convolutional neural network based on the U-net architecture~\cite{RonnebergerFB15}. The probabilities are used to seed watershed and generate an oversegmentation using superpixels. Agglomeration is then performed by the GALA active learning classifier~\cite{nunez2014graph}.

@@

To train our split error classifier, we use the L. Cylinder dataset. We use the first 250 sections of the data for training and validation. For n-fold cross validation, we select one quarter of this data and re-select after each epoch. We minimize cross-entropy loss and update using stochastic gradient descent with Nesterov momentum \cite{nesterov}.
To generate training data, we identify correct regions and split errors in the automatic segmentation by intersection with ground truth regions. This is required since extracellular space is not labeled in the ground truth but in our dense automatic segmentation. 
From these regions, we sample 112,760 correct and 112,760 split error patches with 4-channels as described above. The patches are normalized and to further augment our training data, we rotate patches within each mini-batch by $k*90$ degrees with randomly chosen $k$. The training parameters such as filter size, number of filters, learning rate, and momentum are the result of intuition and experience, studying recent machine learning research, and a brute force parameter search within a limited range (see supplementary material). 
The first row of table~\ref{tab:parameters} lists the final parameters. Our CNN configuration results in approximately 170,000 learnable parameters. We assume that training has converged if the validation loss does not decrease for 50 epochs. We test the CNN by generating a balanced set of 8,780 correct and 8,780 error patches using unseen data of the left cylinder dataset and report testing results in the second row of table~\ref{tab:parameters}.

@@

\subsection{Baseline Comparisons}

\textbf{Interactive proofreading.} A comparison of interactive proofreading tools by Haehn~\etal~ concludes that novices perform best when using Dojo~\cite{haehn_dojo_2014}. We use the publicly available findings of their user study as a baseline comparison. More specifically, we use the data of the Dojo user with the reported best performance.

\textbf{Computer-aided proofreading.} We compare against focused proofreading by Plaza~\cite{focused_proofreading}. Focused proofreading performs graph analysis on output from NeuroProof \cite{neuroproof2013}. For training, we therefore replace GALA in our automatic segmentation pipeline with NeuroProof but use exactly the same input data including membrane probabilities. We obtained the best possible parameters for NeuroProof by consulting the developers and report them in table \ref{tab:parameters}.

### 2016-11-14 paper/introduction.tex

Second, we propose a greedy algorithm for guided proofreading. Possible erroneous regions are sorted by their score, and a correction is generated for each region. Then, a user works through this list of regions and corrections. In a forced choice setting, the user either selects a correction or skips it to advance to the next region. In an automatic setting, errors with a high probability can be automatically corrected first, given an appropriate probability threshold, after which the user would take over. Finally, to test the limits of performance, we create an oracle with knowledge of the ground truth, which only accepts corrections when they improve the segmentation. This equals perfect proofreading.

@@

We state our contributions:
\begin{itemize}
\item A CNN-based boundary classifier for split errors, plus a merge error classifier which inverts the split error classifier. This is used to propose merge error corrections, which removes the need to manually draw the missing edge. These classifiers perform well with small amounts of training data, which is expensive to collect for connectomics data.
\item A guided proofreading approach to correcting segmentation volumes, and an assessment scenario comparing forced-choice interaction with automatic and oracle proofreading.
\item A quantitative user study assessing guided proofreading, which shows that our method is able to reduce segmentation error faster than state-of-the-art semi-automatic tools, across both novice and expert users.
\end{itemize}
Our method applies to all existing automatic segmentation methods which produce a label map. As such, we believe that guided proofreading is a promising direction to proofread segmentations more efficiently, and so help better tackle large volumes of connectomics imagery.

>>>>

Second, we propose a greedy algorithm for guided proofreading. Possible erroneous regions are sorted by their score, and a correction is generated for each region. Then, a user works through this list of regions and corrections. In a forced choice setting, the user either selects a correction or skips it to advance to the next region. In an automatic setting, errors with a high probability can be automatically corrected first, given an appropriate probability threshold, after which the user would take over. Finally, to test the limits of performance, we create an oracle that only accepts corrections improving the segmentation based on knowledge of the ground truth. This equals perfect proofreading.

@@

We state our contributions:
\begin{itemize}
\item A CNN-based boundary classifier for split errors, plus a merge error classifier which inverts the split error classifier. This is used to propose merge error corrections, removing the need to manually draw the missing edge. These classifiers perform well without much training data, which is expensive to collect for connectomics data.
\item A guided proofreading approach to correcting segmentation volumes, and an assessment scenario comparing forced-choice interaction with automatic and oracle proofreading.
\item A quantitative user study assessing guided proofreading, which shows that our method is able to reduce segmentation error faster than state-of-the-art semi-automatic tools, across both novice and expert users.
\end{itemize}
Our method applies to all existing automatic segmentation methods which produce a label map. As such, we believe that guided proofreading is a promising direction to proofread segmentations more efficiently to help better tackle large volumes of connectomics imagery.

### 2016-11-14 paper/method.tex

We build a split error classifier with output $p$ using a convolutional neural network (CNN) to check whether an edge within an existing automatic segmentation is valid ($p=0$) or not ($p=1$). Rather than analyzing every input pixel, the classifier operates only on segment boundaries which requires less pixel context and is faster. In contrast to Bogovic \etal~\cite{BogovicHJ13}, we work with 2D slices rather than 3D volumes. This enables proofreading prior or in parallel to an expensive alignment of individual EM images.
\\~\\
\textbf{Convolutional Neural Network Architecture.} Split error detection of a given boundary is really a binary classification task since the boundary is either correct or erroneous. However, in reality the score $p$ is between 0 and 1. The classification complexity arises from hundreds of different cell types in connectomics data rather than from the classification decision. Intuitively, this yields a wider (meaning more filters) rather than a deeper (meaning more layers) architecture. We explored different architectural configurations - including residual networks~\cite{resnet} - by performing a brute force parameter search and comparing precision and recall (see supplementary materials). Our final CNN configuration for split error detection is composed of four convolutional layers, each followed by max pooling as well as dropout regularization to prevent overfitting due to limited training data. Fig. \ref{fig:architecture} shows the CNN architecture for split error detection.
\\~\\
\textbf{Classifier Inputs.} To train the CNN for split error detection, we take boundary context information into consideration for the decision making process. For this, we use a $75\times75$ pixel patch at the center of an existing boundary. This covers approximately $80\%$ of all boundaries in real-world connectomics data with nanometer resolution. If the boundary edge is not fully covered, we sample up to 10 non-overlapping patches along the boundary and combine the resulting score by weighted averaging based on boundary length coverage per patch. 
Similar to Bogovich~\etal~\cite{BogovicHJ13}, we use grayscale image data, corresponding boundary probabilities, and a single binary mask combining the two neighboring labels as features for our CNN. However, we observed that the boundary probability information generated from EM images is often misleading due to noise or artifacts in the data. This can result in merge errors within the automatic segmentation. To better direct our classifier to train on the true boundary edge, we extract the border between two segments. We then dilate this border by 5 pixels to consider slight edge ambiguities and use this binary mask as an additional feature to create a stacked 4-channel input patch. Fig. \ref{fig:cnn_inputs} shows examples of correct and erroneous feature patches and their corresponding automatic segmentation and ground truth.

\begin{figure}[h]
\begin{center}
  \includegraphics[width=\linewidth]{gfx/cnn_inputs.pdf}
\end{center}
  \vspace{-4mm}
   \caption{Example inputs for learning correct splits and split errors as reflected in the segmentation relative to the ground truth. Image, membrane probabilities, merged binary labels, and a dilated border mask are combined to 4-channel input patches.}
\label{fig:cnn_inputs}
\end{figure}

@@

Identification and correction of merge errors is more challenging than finding and fixing split errors, because we must look inside segmentation regions for missing or incomplete boundaries and then propose the correct boundary. However, we can reuse the same trained CNN for this task. Similar to guided volume editing by Karimov~\etal~\cite{karimov_guided_volume_editing} we generate potential borders within a segment. For each segmentation label, we dilate the label by 20 pixel and generate 50 potential boundaries through the region by randomly placing watershed seed points at opposite sides of the label boundary. For watershed, we use the inverted gray scale EM image as features. This yields 50 candidate splits.

Dilation of the segment prior to watershed is motivated by our observation that the generated split likely attaches to the real membrane boundary. These boundaries are then individually rated using our split error classifier. For this, we invert the probability score such that a correct split (previously encoded as $p=0$) is most likely a candidate for a merge error (now encoded as $p=1$). In other words, if a generated boundary is ranked as correct, it probably should be in the segmentation. Fig. \ref{fig:merge_error} illustrates this procedure.

\begin{figure}[h]
\begin{center}
  \includegraphics[width=\linewidth]{gfx/merge_error.pdf}
\end{center}
  \vspace{-4mm}
   \caption{Merge errors are identified by generating randomly seeded watershed borders within a dilated label segment. These borders then are individually rated using the split error CNN by inverting the probability score. This way, a confident rating for a correct split most likely indicates the missing border of the merge error and can be used for correcting the labeling.}
\label{fig:merge_error}
\end{figure}

@@

We use the proposed classifiers in combination to perform corrections of split and merge errors in automatic segmentations. For this, we first perform merge error detection for all existing segments in a dataset and store the inverted rankings $1-p$ as well as potential corrections. After that, we perform split error detection and store the ranking $p$ for all neighboring segments in the segmentation. We then sort the merge and split error rankings individually from highest to lowest. 
For error correction, we first loop through the potential merge error regions and then through the potential split error regions. During this process, each error is now subject to a yes/no decision which can be provided in different ways: 
\\~\\
\textbf{Selection oracle.} If ground data is available, the selection oracle \textit{knows} whether a possible correction improves an automatic segmentation. This is realized by simply applying the correction and comparing the outcome using a defined measure. The oracle only accepts corrections which improve the automatic segmentation - others get 
discarded. This equals perfect proofreading.
\\~\\
\textbf{Automatic selection with threshold.} The decision whether to accept or reject a potential correction is done by comparing rankings to a threshold $p_t$. If the inverted score $1-p$ of a merge error is higher than a threshold $1-p_t$, the correction is accepted. Similarly, a correction is accepted for a split error if the ranking $p$ is higher than $p_t$. Our experiments have shown that the threshold $p_t$ is the same for merge and split errors which makes sense for a balanced classifier.
\\~\\
\textbf{Forced choice setting.} A user is presented with the choices of either accepting or rejecting a correction. This way, all potential split errors are looked at. Inspecting all merge errors is not possible for users due to the sheer amount of generated borders. We therefor only present merge errors which satisfy $1-p_t$. 
\\~\\
In all cases, a decision has to be made to advance to the next possible erroneous region. If a merge error correction was accepted, the newly found boundary is added to the segmentation data. This partially updates the merge error and split error ranking in respect of the new segment. If a split error correction was accepted, two segments are merged in the segmentation data and the disappearing segment is removed from all error rankings. We then perform merge error detection on the now larger segment and update the ranking. We also update the split error rankings to include all new neighbors and re-sort. The error with the next highest ranking is now subject to the yes/no decision.

@@

Guided proofreading is integrated into an existing workflow for large connectomics data. The system is web-based and is designed with a minimalistic user interface showing three components. We show the outline of the current labeling of a cell boundary and its proposed correction on top of the EM image data. For the user, it is not possible to distinguish the current labeling and the proposed correction to avoid selection bias. We also show a solid overlay of the current and the proposed labeling. In addition, we show the image without overlays to provide an unoccluded view. User interaction is simple and involves one mouse click on either the current labeling or the correction. After interaction, the next potential error is shown. Figure \ref{fig:ui} shows the user interface.

\begin{figure}[h]
\begin{center}
  \includegraphics[width=\linewidth]{gfx/user_interface_split.pdf}
\end{center}
  \vspace{-4mm}
   \caption{Segmentation correction with the guided proofreading user interface. An image without overlays is shown on the left. A split error (right) and its correction (center) are the possible choices for the user. Hovering highlights the current selection with a yellow border and a mouse click confirms it and advances to the next potential error.}
\label{fig:ui}
\end{figure}

>>>>

We build a split error classifier with output $p$ using a convolutional neural network (CNN) to check whether an edge within an existing automatic segmentation is valid ($p=0$) or not ($p=1$). Rather than analyzing every input pixel, the classifier operates only on segment boundaries which requires less pixel context and is faster. In contrast to Bogovic \etal~\cite{BogovicHJ13}, we work with 2D slices rather than 3D volumes. This enables proofreading prior or in parallel to a computationally expensive alignment of individual EM images.
\\~\\
\textbf{Convolutional Neural Network Architecture.} Split error detection of a given boundary is really a binary classification task since the boundary is either correct or erroneous. However, in reality the score $p$ is between 0 and 1. The classification complexity arises from hundreds of different cell types in connectomics data rather than from the classification decision itself. Intuitively, this yields a wider architecture with more filters rather than a deeper architecture with more layers. We explored different architectural configurations - including residual networks~\cite{resnet} - by performing a brute force parameter search and comparing precision and recall (see supplementary materials). Our final CNN configuration for split error detection is composed of four convolutional layers, each followed by max pooling as well as dropout regularization to prevent overfitting due to limited training data. Fig. \ref{fig:architecture} shows the CNN architecture for split error detection.
\\~\\
\textbf{Classifier Inputs.} To train the CNN for split error detection, we take boundary context information into consideration for the decision making process. For this, we use a $75\times75$ pixel patch at the center of an existing boundary. This covers approximately $80\%$ of all boundaries in real-world connectomics data with nanometer resolution. If the boundary length is not fully covered, we sample up to 10 non-overlapping patches along the boundary and combine the resulting score by weighted averaging based on boundary length coverage per patch. 
Similar to Bogovich~\etal~\cite{BogovicHJ13}, we use grayscale image data, corresponding boundary probabilities, and a single binary mask combining the two neighboring labels as features for our CNN. However, we observed that the boundary probability information generated from EM images is often misleading due to noise or artifacts in the data. This can result in merge errors within the automatic segmentation. To better direct our classifier to train on the true boundary, we extract the border between two segments. We then dilate this border by 5 pixels to consider slight edge ambiguities and use this binary mask as an additional feature to create a stacked 4-channel input patch. Fig. \ref{fig:cnn_inputs} shows examples of correct and erroneous feature patches and their corresponding automatic segmentation and ground truth.

\begin{figure}[h]
\begin{center}
  \includegraphics[width=\linewidth]{gfx/cnn_inputs.pdf}
\end{center}
 % \vspace{-4mm}
   \caption{Example inputs for learning correct splits and split errors as reflected in the segmentation relative to the ground truth. Image, membrane probabilities, merged binary labels, and a dilated border mask are combined to 4-channel input patches.}
\label{fig:cnn_inputs}
\end{figure}

@@

Identification and correction of merge errors is more challenging than finding and fixing split errors, because we must look inside segmentation regions for missing or incomplete boundaries and then propose the correct boundary. However, we can reuse the same trained CNN for this task. Similar to guided volume editing by Karimov~\etal~\cite{karimov_guided_volume_editing} we generate potential borders within a segment. For each segmentation label, we dilate the label by 20 pixel and generate 50 potential boundaries through the region by randomly placing watershed seed points at opposite sides of the label boundary. For watershed, we use the inverted grayscale EM image as features. This yields 50 candidate splits.

Dilation of the segment prior to watershed is motivated by our observation that the generated split tends to attach to the real membrane boundary. These boundaries are then individually rated using our split error classifier. For this, we invert the probability score such that a correct split (previously encoded as $p=0$) is most likely a candidate for a merge error (now encoded as $p=1$). In other words, if a generated boundary is ranked as correct, it probably should be in the segmentation. Fig. \ref{fig:merge_error} illustrates this procedure.

\begin{figure}[h]
\begin{center}
  \includegraphics[width=\linewidth]{gfx/merge_error.pdf}
\end{center}
%  \vspace{-4mm}
   \caption{Merge errors are identified by generating randomly seeded watershed borders within a dilated label segment. These borders then are individually rated using the split error CNN by inverting the probability score. This way, a confident rating for a correct split most likely indicates the missing border of the merge error and can be used for correcting the labeling.}
\label{fig:merge_error}
\end{figure}

@@

We use the proposed classifiers in combination to perform corrections of split and merge errors in automatic segmentations. For this, we first perform merge error detection for all existing segments in a dataset and store the inverted rankings $1-p$ as well as potential corrections. After that, we perform split error detection and store the ranking $p$ for all neighboring segments in the segmentation. We then sort the merge and split error rankings individually from highest to lowest. 
For error correction, we first loop through the potential merge error regions and then through the potential split error regions. During this process, each error is now subject to a yes/no decision which can be provided in different ways: 
\\~\\
\textbf{Selection oracle.} If ground truth data is available, the selection oracle \textit{knows} whether a possible correction improves an automatic segmentation. This is realized by simply comparing the outcome of a correction using a defined measure. The oracle only accepts corrections which improve the automatic segmentation - others get 
discarded. This equals perfect proofreading.
\\~\\
\textbf{Automatic selection with threshold.} The decision whether to accept or reject a potential correction is done by comparing rankings to a threshold $p_t$. If the inverted score $1-p$ of a merge error is higher than a threshold $1-p_t$, the correction is accepted. Similarly, a correction is accepted for a split error if the ranking $p$ is higher than $p_t$. Our experiments have shown that the threshold $p_t$ is the same for merge and split errors which makes sense for a balanced classifier, trained on equal numbers of correct and error patches.
\\~\\
\textbf{Forced choice setting.} A user is presented with the choices of either accepting or rejecting a correction. This way, all potential split errors are seen. Inspecting all merge errors is not possible for users due to the sheer amount of generated borders. We therefore only present merge errors which satisfy $1-p_t$. 
\\~\\
In all cases, a decision has to be made to advance to the next possible erroneous region. If a merge error correction was accepted, the newly found boundary is added to the segmentation data. This partially updates the merge error and split error ranking with respect to the new segment. If a split error correction was accepted, two segments are merged in the segmentation data and the disappearing segment is removed from all error rankings. We then perform merge error detection on the now larger segment and update the ranking. We also update the split error rankings to include all new neighbors and re-sort. The error with the next highest ranking is now subject to the yes/no decision.

@@

Guided proofreading is integrated into an existing workflow for large connectomics data. The system is web-based and is designed with a minimalistic user interface showing three components. We show the outline of the current labeling of a cell boundary and its proposed correction overlaying the EM image data. For the user, it is not possible to distinguish the current labeling and the proposed correction to avoid selection bias. We also show a solid overlay of the current and the proposed labeling. In addition, we show the image without overlays to provide an unoccluded view. User interaction is simple and involves one mouse click on either the current labeling or the correction. After interaction, the next potential error is shown. Figure \ref{fig:ui} shows the user interface.

\begin{figure}[h]
\begin{center}
  \includegraphics[width=\linewidth]{gfx/user_interface_split.pdf}
\end{center}
  \vspace{-4mm}
   \caption{Segmentation correction with the guided proofreading user interface. An image without overlays is shown on the left. A split error (right) and its correction (center) are the possible choices for the user. Hovering highlights the current selection with a yellow border, and a mouse click confirms it by advancing to the next potential error.}
\label{fig:ui}
\end{figure}
